The Impact of Educational Expenses of New Coders

### 2021-04-18 outputs/paper/paper.Rmd
Add custom function for RMSE

library(tidyverse)
library(dplyr)
library(janitor)
library(stargazer)
library(psych)
# install.packages("here")
library(here)
# install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
# install.packages("QuantPsyc")
library(QuantPsyc)
library(car)
library(kableExtra)
# install.packages("forecast")
library(forecast)
```

@@

## Model validation
```{r}
#### Line plot for fitted values
plot(dfNewCoders$MoneyForLearning)
lines(multiReg1$fitted.values, col = "red")
lines(multiReg2$fitted.values, col = "blue")
lines(multiReg3$fitted.values, col = "green")

```{r}
#### RMSE ####
forecast::accuracy(multiReg1)
```

@@

RMSE(multiReg1$residuals)

>>>>

library(tidyverse)
library(dplyr)
library(janitor)
library(stargazer)
library(psych)
# install.packages("here")
library(here)
# install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
# install.packages("QuantPsyc")
library(QuantPsyc)
library(car)
library(kableExtra)
```

@@

## Model validation with RMSE

@@

RMSE(multiReg1$residuals)
RMSE(multiReg2$residuals)
RMSE(multiReg3$residuals)

# Model3 has the lowest RMSE among the 3 models => Model3 is the best!
